Why aren't significance tests commonly used for linear regression diagnostics?

### 2022-12-13 paper_comparison/paper_comparison/paper_comparison.Rmd
swap power cmp and p-value cmp
fix plot in power cmp

@@

Figure \ref{fig:polypower} show the estimated power of visual test on lineups produced by the non-linearity model with the $X_{raw}$ following a uniform distribution, against the natural logarithm of the effect $log_e(E)$ with comparison to the power of an exact test - F-test, and two other residual-based conventional tests commonly used in regression diagnostics but for testing heteroskedasticity and non-normality respectively. At the bottom of the figure \ref{fig:polypower}, there are a sequence of example residuals plots with increasing levels of $log_e(E)$. Readers can evaluate them from left to right and determine at which level the departure from a good residual plot becomes detectable.

Figure \ref{fig:heterpower} is similar to Figure \ref{fig:polypower}, but shows corresponding information on lineups produced by the heteroskedasticity model. In this scenario, the visual test is compared to an approximate test - Breusch-Pagan test, and two other inappropriate tests - F-test and Shapiro-Wilk test.

```{r eval = FALSE}
filter(vi_survey, type == "polynomial") %>%
  filter(x_dist == "uniform") %>%
  mutate(log_es = abs(log(effect_size) - 4)) %>%
  arrange(log_es) %>%
  View()
```

```{r power-poly-uniform, fig.cap = "...", eval = FALSE}
vi_survey %>%
  filter(x_dist == "uniform") %>%
  group_by(unique_lineup_id) %>%
  summarise(across(everything(), first)) %>%
  filter(type == "polynomial") %>%
  filter(!null_lineup) %>%
  filter(!attention_check) %>%
  mutate(reject_dirichlet = as.numeric(p_value <= 0.05)) %>%
  mutate(log_effect_size = log(effect_size)) %>%
  ggplot() +
  geom_smooth(aes(log_effect_size, reject_dirichlet, col = "Visual test"), method = "glm", method.args = list(family = binomial), se = FALSE) +
  stat_smooth(geom = "line", 
              data = ~boot_y(.x, reject_dirichlet, times = 500), 
              aes(log_effect_size, reject_dirichlet, group = boot_id, col = "Visual test"), 
              method = "glm", 
              method.args = list(family = binomial), 
              se = FALSE, 
              alpha = 0.03) +
  geom_smooth(data = mutate(poly_conv_sim, log_effect_size = log(effect_size)) %>%
                filter(x_dist == "uniform") %>%
                pivot_longer(F_p_value:SW_p_value) %>%
                mutate(name = gsub("_p_value", " test", name)), 
              aes(log_effect_size, as.numeric(value < 0.05), col = name), 
              method = "glm", 
              method.args = list(family = binomial),
              se = FALSE) +
  geom_point(aes(log_effect_size, prop_detect), alpha = 0.3) + geom_point(data = ~filter(.x, unique_lineup_id %in% c("poly_166", "poly_269", "poly_396", "poly_574")), aes(log_effect_size, prop_detect), alpha = 1, col = "red", size = 2) +
  theme_light(base_size = 5) +
  scale_color_brewer(palette = "Dark2", direction = -1) +
  xlab("Natural logarithm of effect size") +
  ylab("Power") -> p

VI_MODEL$plot_lineup(vi_lineup[["poly_166"]]$data, 
                     remove_grid_line = TRUE, 
                     theme = theme_light(base_size = 5),
                     remove_axis = TRUE,
                     size = 0.1) + 
  ggtitle(bquote(log[e](E) %~~% 1~","~"F-test p-value" == .(format(filter(vi_survey, unique_lineup_id == "poly_166")$conventional_p_value[1], digits = 3))~", Visual p-value " == .(format(filter(vi_survey, unique_lineup_id == "poly_166")$p_value[1], digits = 3)))) -> p1

VI_MODEL$plot_lineup(vi_lineup[["poly_269"]]$data,
                     remove_grid_line = TRUE, 
                     theme = theme_light(base_size = 5),
                     remove_axis = TRUE,
                     size = 0.1) + 
  ggtitle(bquote(log[e](E) %~~% 2~","~"F-test p-value" == .(format(filter(vi_survey, unique_lineup_id == "poly_269")$conventional_p_value[1], digits = 3))~", Visual p-value " == .(format(filter(vi_survey, unique_lineup_id == "poly_269")$p_value[1], digits = 3)))) -> p2

VI_MODEL$plot_lineup(vi_lineup[["poly_396"]]$data, 
                     remove_grid_line = TRUE, 
                     theme = theme_light(base_size = 5),
                     remove_axis = TRUE, 
                     size = 0.1) + 
  ggtitle(bquote(log[e](E) %~~% 3~","~"F-test p-value" == .(format(filter(vi_survey, unique_lineup_id == "poly_396")$conventional_p_value[1], digits = 3))~", Visual p-value " == .(format(filter(vi_survey, unique_lineup_id == "poly_396")$p_value[1], digits = 3)))) -> p3

VI_MODEL$plot_lineup(vi_lineup[["poly_574"]]$data, 
                     remove_grid_line = TRUE, 
                     theme = theme_light(base_size = 5),
                     remove_axis = TRUE,
                     size = 0.1) + 
  ggtitle(bquote(log[e](E) %~~% 4~","~"F-test p-value" == .(format(filter(vi_survey, unique_lineup_id == "poly_574")$conventional_p_value[1], digits = 3))~", Visual p-value " == .(format(filter(vi_survey, unique_lineup_id == "poly_574")$p_value[1], digits = 3)))) -> p4

design <- c(patchwork::area(1, 1, 1, 8),
            patchwork::area(2, 1, 2, 4), 
            patchwork::area(2, 5, 2, 8), 
            patchwork::area(3, 1, 3, 4), 
            patchwork::area(3, 5, 3, 8))

patchwork::wrap_plots(p, B = p1, C = p2, D = p3, E = p4, design = design)
```

```{r}
p <- vi_survey %>%
  filter(x_dist == "uniform") %>%
  group_by(unique_lineup_id) %>%
  summarise(across(everything(), first)) %>%
  filter(type == "polynomial") %>%
  filter(!null_lineup) %>%
  filter(!attention_check) %>%
  mutate(reject_dirichlet = as.numeric(p_value <= 0.05)) %>%
  mutate(log_effect_size = log(effect_size)) %>%
  ggplot() +
  geom_smooth(aes(log_effect_size, reject_dirichlet, col = "Visual test"), method = "glm", method.args = list(family = binomial), se = FALSE) +
  stat_smooth(geom = "line", 
              data = ~boot_y(.x, reject_dirichlet, times = 500), 
              aes(log_effect_size, reject_dirichlet, group = boot_id, col = "Visual test"), 
              method = "glm", 
              method.args = list(family = binomial), 
              se = FALSE, 
              alpha = 0.03) +
  geom_smooth(data = mutate(poly_conv_sim, log_effect_size = log(effect_size)) %>%
                select(-(RESET5_p_value:RESET10_p_value)) %>%
                select(-RESET3_p_value, -F_p_value) %>%
                rename(RESET_p_value = RESET4_p_value) %>%
                filter(x_dist == "uniform") %>%
                pivot_longer(RESET_p_value:SW_p_value) %>%
                mutate(name = gsub("_p_value", " test", name)), 
              aes(log_effect_size, as.numeric(value < 0.05), col = name), 
              method = "glm", 
              method.args = list(family = binomial),
              se = FALSE) +
  geom_point(data = ~.x %>% 
               group_by(log_effect_size, reject_dirichlet) %>% 
               summarise(num_response = n()),
             aes(log_effect_size, reject_dirichlet, size = factor(num_response)), alpha = 0.3)  +
  geom_segment(data = data.frame(xi = es), aes(x = xi, xend = xi, y = 0, yend = 1), alpha = 0.4, linetype = 2) +
  theme_light(base_size = 5) +
  scale_color_manual(values = rev(rcartocolor::carto_pal(4, "Vivid"))) +
  scale_size_manual(values = c(1, 2, 3)) +
  xlab("Effect size (log e)") +
  ylab("Power") +
  labs(col = "", size = "#lineups")

```{r polypower, fig.height = 3, fig.width = 5, fig.cap="Comparison of power between different tests for nonlinear patterns. Main plot shows the power curves, with dots indicating human evaluations of lineups. Small row of plots shows typical residual plots corresponding to specific effect sizes, marked by dashed lines in main plot. Where would you draw the line of too much nonlinearity in the residuals? For the F test this is around log effect size 0.5, but for the visual test it is around 3."}
patchwork::wrap_plots(append(plist, list(p), 
                             after = 0), 
                      design = map(1:11, ~patchwork::area(21, .x, 22, .x)) %>%
                        reduce(c) %>%
                        c(patchwork::area(3, 1, 20, 11), .))
```

```{r}
p <- vi_survey %>%
  filter(x_dist == "uniform") %>%
  group_by(unique_lineup_id) %>%
  summarise(across(everything(), first)) %>%
  filter(type == "heteroskedasticity") %>%
  filter(!null_lineup) %>%
  filter(!attention_check) %>%
  mutate(reject_dirichlet = as.numeric(p_value <= 0.05)) %>%
  mutate(log_effect_size = log(effect_size)) %>%
  ggplot() +
  geom_smooth(aes(log_effect_size, reject_dirichlet, col = "Visual test"), method = "glm", method.args = list(family = binomial), se = FALSE) +
  stat_smooth(geom = "line", 
              data = ~boot_y(.x, reject_dirichlet, times = 500), 
              aes(log_effect_size, reject_dirichlet, group = boot_id, col = "Visual test"), 
              method = "glm", 
              method.args = list(family = binomial), 
              se = FALSE, 
              alpha = 0.03) +
  geom_smooth(data = mutate(heter_conv_sim, log_effect_size = log(effect_size)) %>%
                filter(x_dist == "uniform") %>%
                select(-(RESET5_p_value:RESET10_p_value)) %>%
                select(-RESET3_p_value, -F_p_value) %>%
                rename(RESET_p_value = RESET4_p_value) %>%
                pivot_longer(RESET_p_value:SW_p_value) %>%
                mutate(name = gsub("_p_value", " test", name)), 
              aes(log_effect_size, as.numeric(value < 0.05), col = name), 
              method = "glm", 
              method.args = list(family = binomial),
              se = FALSE) +
  geom_point(data = ~.x %>% 
               group_by(log_effect_size, reject_dirichlet) %>% 
               summarise(num_response = n()),
             aes(log_effect_size, reject_dirichlet, size = factor(num_response)), alpha = 0.3)  +
  geom_segment(data = data.frame(xi = es), aes(x = xi, xend = xi, y = 0, yend = 1), alpha = 0.4, linetype = 2) +
  theme_light(base_size = 5) +
  scale_color_manual(values = rev(rcartocolor::carto_pal(4, "Vivid"))) +
  scale_size_manual(values = c(1, 2, 3)) +
  xlab("Effect size (log e)") +
  ylab("Power") +
  labs(col = "", size = "#lineups")

```{r heterpower, fig.height = 3, fig.width = 5, fig.cap="..."}
patchwork::wrap_plots(append(plist, list(p), after = 0), 
                      design = map(1:11, ~patchwork::area(21, .x, 22, .x)) %>%
                        reduce(c) %>%
                        c(patchwork::area(3, 1, 20, 11), .))
```

>>>>

Figure \ref{fig:polypower} shows the estimated power of visual test on lineups produced by the non-linearity model with $X_{raw} \sim U(-1,1)$, against the natural logarithm of the effect $log_e(E)$ with comparison to the power of an exact test - RESET test, and two other residual-based conventional tests commonly used in regression diagnostics but for testing heteroskedasticity and non-normality respectively. At the bottom of the figure \ref{fig:polypower}, there are a sequence of example residuals plots with increasing levels of $log_e(E)$. Readers can evaluate them from left to right and determine at which level the departure from a good residual plot becomes detectable.

Figure \ref{fig:heterpower} is similar to Figure \ref{fig:polypower}, but shows corresponding information on lineups produced by the heteroskedasticity model. In this scenario, the visual test is compared to an approximate test - Breusch-Pagan test, and two other inappropriate tests - RESET test and Shapiro-Wilk test.

```{r}
p <- vi_survey %>%
  filter(x_dist == "uniform") %>%
  group_by(unique_lineup_id) %>%
  summarise(across(everything(), first)) %>%
  filter(type == "polynomial") %>%
  filter(!null_lineup) %>%
  filter(!attention_check) %>%
  mutate(reject_dirichlet = as.numeric(p_value <= 0.05)) %>%
  mutate(log_effect_size = log(effect_size)) %>%
  ggplot() +
  geom_smooth(aes(log_effect_size, reject_dirichlet, col = "Visual test"), method = "glm", method.args = list(family = binomial), se = FALSE) +
  stat_smooth(geom = "line", 
              data = ~boot_y(.x, reject_dirichlet, times = 500), 
              aes(log_effect_size, reject_dirichlet, group = boot_id, col = "Visual test"), 
              method = "glm", 
              method.args = list(family = binomial), 
              se = FALSE, 
              alpha = 0.03) +
  geom_smooth(data = mutate(poly_conv_sim, log_effect_size = log(effect_size)) %>%
                select(-(RESET5_p_value:RESET10_p_value)) %>%
                select(-RESET3_p_value, -F_p_value) %>%
                rename(RESET_p_value = RESET4_p_value) %>%
                filter(x_dist == "uniform") %>%
                pivot_longer(RESET_p_value:SW_p_value) %>%
                mutate(name = gsub("_p_value", " test", name)), 
              aes(log_effect_size, as.numeric(value < 0.05), col = name), 
              method = "glm", 
              method.args = list(family = binomial),
              se = FALSE) +
  geom_point(data = ~.x %>% 
               group_by(log_effect_size, reject_dirichlet) %>% 
               summarise(num_response = n()),
             aes(log_effect_size, reject_dirichlet, size = factor(num_response)), alpha = 0.3)  +
  geom_segment(data = data.frame(xi = es), aes(x = xi, xend = xi, y = 0, yend = 1), alpha = 0.3, col = "grey") +
  theme_light(base_size = 5) +
  scale_color_manual(values = rev(rcartocolor::carto_pal(4, "Vivid"))) +
  scale_size_manual(values = c(1, 2, 3)) +
  scale_x_continuous(breaks = seq(0, 5, 0.5), minor_breaks = NULL) +
  xlab("Effect size (log e)") +
  ylab("Power") +
  labs(col = "", size = "#lineups")

```{r polypower, fig.height = 3, fig.width = 5, fig.cap="Comparison of power between different tests for non-linear patterns. Main plot shows the power curves, with dots indicating human evaluations of lineups. Small row of plots shows typical residual plots corresponding to specific effect sizes, marked by dashed lines in main plot. Where would you draw the line of too much non-linearity in the residuals? For the RESET test this is around log effect size 1, but for the visual test it is around 3."}
patchwork::wrap_plots(append(plist, list(p), 
                             after = 0), 
                      design = map(1:11, ~patchwork::area(21, .x, 22, .x)) %>%
                        reduce(c) %>%
                        c(patchwork::area(3, 1, 20, 11), .))
```

```{r}
p <- vi_survey %>%
  filter(x_dist == "uniform") %>%
  group_by(unique_lineup_id) %>%
  summarise(across(everything(), first)) %>%
  filter(type == "heteroskedasticity") %>%
  filter(!null_lineup) %>%
  filter(!attention_check) %>%
  mutate(reject_dirichlet = as.numeric(p_value <= 0.05)) %>%
  mutate(log_effect_size = log(effect_size)) %>%
  ggplot() +
  geom_smooth(aes(log_effect_size, reject_dirichlet, col = "Visual test"), method = "glm", method.args = list(family = binomial), se = FALSE) +
  stat_smooth(geom = "line", 
              data = ~boot_y(.x, reject_dirichlet, times = 500), 
              aes(log_effect_size, reject_dirichlet, group = boot_id, col = "Visual test"), 
              method = "glm", 
              method.args = list(family = binomial), 
              se = FALSE, 
              alpha = 0.03) +
  geom_smooth(data = mutate(heter_conv_sim, log_effect_size = log(effect_size)) %>%
                filter(x_dist == "uniform") %>%
                select(-(RESET5_p_value:RESET10_p_value)) %>%
                select(-RESET3_p_value, -F_p_value) %>%
                rename(RESET_p_value = RESET4_p_value) %>%
                pivot_longer(RESET_p_value:SW_p_value) %>%
                mutate(name = gsub("_p_value", " test", name)), 
              aes(log_effect_size, as.numeric(value < 0.05), col = name), 
              method = "glm", 
              method.args = list(family = binomial),
              se = FALSE) +
  geom_point(data = ~.x %>% 
               group_by(log_effect_size, reject_dirichlet) %>% 
               summarise(num_response = n()),
             aes(log_effect_size, reject_dirichlet, size = factor(num_response)), alpha = 0.3)  +
  geom_segment(data = data.frame(xi = es), aes(x = xi, xend = xi, y = 0, yend = 1), alpha = 0.3, col = "grey") +
  theme_light(base_size = 5) +
  scale_color_manual(values = rev(rcartocolor::carto_pal(4, "Vivid"))) +
  scale_x_continuous(breaks = seq(0, 5, 0.5), minor_breaks = NULL) +
  scale_size_manual(values = c(1, 2, 3)) +
  xlab("Effect size (log e)") +
  ylab("Power") +
  labs(col = "", size = "#lineups")

```{r heterpower, fig.height = 3, fig.width = 5, fig.cap="Comparison of power between different tests for heteroskedasticity patterns. Main plot shows the power curves, with dots indicating human evaluations of lineups. Small row of plots shows typical residual plots corresponding to specific effect sizes, marked by dashed lines in main plot. Where would you draw the line of too much heteroskedasticity in the residuals? For the BP test this is around log effect size 1.5, but for the visual test it is around 3."}
patchwork::wrap_plots(append(plist, list(p), after = 0), 
                      design = map(1:11, ~patchwork::area(21, .x, 22, .x)) %>%
                        reduce(c) %>%
                        c(patchwork::area(3, 1, 20, 11), .))
```

@@

### 2022-12-13 paper_comparison/paper_comparison/paper_comparison.tex
swap power cmp and p-value cmp
fix plot in power cmp

@@

Figure \ref{fig:polypower} show the estimated power of visual test on
lineups produced by the non-linearity model with the \(X_{raw}\)
following a uniform distribution, against the natural logarithm of the
effect \(log_e(E)\) with comparison to the power of an exact test -
F-test, and two other residual-based conventional tests commonly used in
regression diagnostics but for testing heteroskedasticity and
non-normality respectively. At the bottom of the figure
\ref{fig:polypower}, there are a sequence of example residuals plots
with increasing levels of \(log_e(E)\). Readers can evaluate them from
left to right and determine at which level the departure from a good
residual plot becomes detectable.

Figure \ref{fig:heterpower} is similar to Figure \ref{fig:polypower},
but shows corresponding information on lineups produced by the
heteroskedasticity model. In this scenario, the visual test is compared
to an approximate test - Breusch-Pagan test, and two other inappropriate
tests - F-test and Shapiro-Wilk test.

\caption{Comparison of power between different tests for nonlinear patterns. Main plot shows the power curves, with dots indicating human evaluations of lineups. Small row of plots shows typical residual plots corresponding to specific effect sizes, marked by dashed lines in main plot. Where would you draw the line of too much nonlinearity in the residuals? For the F test this is around log effect size 0.5, but for the visual test it is around 3.}\label{fig:polypower}
\end{figure}

\caption{...}\label{fig:heterpower}
\end{figure}

>>>>

Figure \ref{fig:polypower} shows the estimated power of visual test on
lineups produced by the non-linearity model with
\(X_{raw} \sim U(-1,1)\), against the natural logarithm of the effect
\(log_e(E)\) with comparison to the power of an exact test - RESET test,
and two other residual-based conventional tests commonly used in
regression diagnostics but for testing heteroskedasticity and
non-normality respectively. At the bottom of the figure
\ref{fig:polypower}, there are a sequence of example residuals plots
with increasing levels of \(log_e(E)\). Readers can evaluate them from
left to right and determine at which level the departure from a good
residual plot becomes detectable.

Figure \ref{fig:heterpower} is similar to Figure \ref{fig:polypower},
but shows corresponding information on lineups produced by the
heteroskedasticity model. In this scenario, the visual test is compared
to an approximate test - Breusch-Pagan test, and two other inappropriate
tests - RESET test and Shapiro-Wilk test.

\caption{Comparison of power between different tests for non-linear patterns. Main plot shows the power curves, with dots indicating human evaluations of lineups. Small row of plots shows typical residual plots corresponding to specific effect sizes, marked by dashed lines in main plot. Where would you draw the line of too much non-linearity in the residuals? For the RESET test this is around log effect size 1, but for the visual test it is around 3.}\label{fig:polypower}
\end{figure}

\caption{Comparison of power between different tests for heteroskedasticity patterns. Main plot shows the power curves, with dots indicating human evaluations of lineups. Small row of plots shows typical residual plots corresponding to specific effect sizes, marked by dashed lines in main plot. Where would you draw the line of too much heteroskedasticity in the residuals? For the BP test this is around log effect size 1.5, but for the visual test it is around 3.}\label{fig:heterpower}
\end{figure}

@@
